Curiosity-Driven Development of Tool Use Precursors: a Robotic Model

### 2016-02-01 cogsci2016/paper.tex
abstract

\begin{abstract}
This is the abstract.\\
This is the abstract.\\
This is the abstract.\\
This is the abstract.\\
This is the abstract.\\
This is the abstract.\\
This is the abstract.\\

>>>>

\begin{abstract}
Studies of child development of tool use precursors show successive but overlapping phases of qualitatively different types of behaviours.
We hypothethize that two mechanisms in particular play a role in the structuring of these phases: the intrinsic motivation to explore and the representation used to encode sensorimotor experience.
Previous models show how curiosity-driven learning mechanisms could allow the emergence of developmental trajectories.
We build upon those models and present the HACOB (Hierarchical Active Curiosity-driven mOdel Babbling) architecture 
that actively chooses which sensorimotor model to train in a hierarchy a models representing the environmental structure.
We define a robotic arm in a $2$D environment with objects and we show that overlapping phases of behaviour are autonomously emerging in active model babbling conditions.
To our knowledge, this is the first model of the curiosity-driven development of tool use and the first to actively explore non-optimal methods to reach a goal, in accordance with Siegler's overlapping waves theory.
